NodIO: a framework and architecture for pool-based evolutionary computation

### 2016-05-03 EvoSoft16/nodio-evosoft16.tex
ACM Classification added
Please compile and check, I don’t have latex here.

>>>>

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010178.10010219</concept_id>
<concept_desc>Computing methodologies~Distributed artificial intelligence</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010219.10010220</concept_id>
<concept_desc>Computing methodologies~Multi-agent systems</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Computing methodologies~Distributed artificial intelligence}
\ccsdesc[300]{Computing methodologies~Multi-agent systems}
